Staged Abstract Interpreters

### 2019-04-06 paper/30_stageconc.tex
misc

For the example we introduced in Section \ref{intro}, we have identified @b@ will 
be known later. To specialize it we write a function @snippet@ that provides a 
concrete value @x@ for @x@. After this, we may instantiate an @DslDriver@ object 
which provide the specialized program.

\begin{lstlisting}
  new DslDriver[Int, Int] {
    def power(b: Rep[Int], x: Int): Rep[Int] = if (x == 0) 1 else b * power(b, x-1)
    def snippet(x: Rep[Int]): Rep[Int] = power(x, 5)
  }
\end{lstlisting}

>>>>

For the example we introduced in Section \ref{intro}, we have identified @b@ will 
be known later. To specialize it we write a function @snippet@ that provides a 
concrete value for @x@. After this, we may instantiate an @DslDriver@ object 
which provide the specialized program.

\begin{lstlisting}
  new DslDriver[Int, Int] {
    def power(b: Rep[Int], x: Int): Rep[Int] = if (x == 0) 1 else b * power(b, x-1)
    def snippet(b: Rep[Int]): Rep[Int] = power(b, 5)
  }
\end{lstlisting}
